### 2017-07-21 README.Rmd

```
mtcars %>%
  specify(response = mpg) %>% # alt: mpg ~ NULL (or mpg ~ 1)
  hypothesize(null = "point", Med = 26) %>% 
  generate(reps = 100, type = "bootstrap") %>% 
  calculate(stat = "median")
```

>>>>

```
mtcars %>%
  specify(response = mpg) %>% # alt: mpg ~ NULL (or mpg ~ 1)
  hypothesize(null = "point", med = 26) %>% 
  generate(reps = 100, type = "bootstrap") %>% 
  calculate(stat = "median")
```

### 2017-07-21 examples/flights_examples.Rmd

```{r}
fli_small %>%
  specify(response = arr_delay) %>% # alt: arr_delay ~ NULL (or arr_delay ~ 1)
  hypothesize(null = "point", mu = 50) %>% 
  generate(reps = params$rep_times, type = "bootstrap") %>% 
  calculate(stat = "mean", na.rm = TRUE)
```

@@

```{r}
fli_small %>%
  specify(response = arr_delay) %>% # alt: arr_delay ~ NULL (or arr_delay ~ 1)
  hypothesize(null = "point", med = 55) %>%
  generate(reps = params$rep_times, type = "bootstrap") %>%
  calculate(stat = "median", na.rm = TRUE)
```

>>>>

```{r}
fli_small %>%
  specify(response = arr_delay) %>% # alt: arr_delay ~ NULL (or arr_delay ~ 1)
  hypothesize(null = "point", mu = 0) %>% 
  generate(reps = params$rep_times, type = "bootstrap") %>% 
  calculate(stat = "mean", na.rm = TRUE)
```

@@

```{r}
fli_small %>%
  specify(response = arr_delay) %>% # alt: arr_delay ~ NULL (or arr_delay ~ 1)
  hypothesize(null = "point", med = 0) %>%
  generate(reps = params$rep_times, type = "bootstrap") %>%
  calculate(stat = "median", na.rm = TRUE)
```

### 2017-07-21 examples/profiles_examples.Rmd

```{r}
prof_small %>%
  specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
  hypothesize(null = "point", Med = 55) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "median") %>% 
  visualize()
```

>>>>

```{r}
prof_small %>%
  specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
  hypothesize(null = "point", med = 55) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "median") %>% 
  visualize()
```
